Fast Algorithms for Intersection of Non-matching Grids Using \plucker coordinates.

### 2016-09-30 paper_intersections.tex
Benchmarks - add intro,sw,ngh, minor fixes.

\vspace{2ex}
\begin{minipage}{\textwidth}
    \centering
    \hspace{-30pt}
  \begin{minipage}[b]{0.44\textwidth}
    \centering
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}[b]{l|l}
            algorithm, 2D-3D& FLOPs\\
                      & estimate\\
            \hline\\
            parametric plane & 585\\
            normal plane (reuse) & 765\\
            Moller and Trumbore & 783\\
            Pl\"ucker (reuse) & 306
    \end{tabular}
    \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
                      Only 2D-3D case considered.}
    \label{tab:fundamental_flops}
    \notePE{comment on different strategies}\noteJB{Rather put into text. I shall comment that.}
  \end{minipage}
  \hfil
  \begin{minipage}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{\figpath intersections_fundamental_speed.pdf}

    \captionof{figure}{Efficiency of \plucker approach compared to the legacy \ngh code.}
    \label{fig:fundamental_speed}
    \end{minipage}
\end{minipage}
\vspace{2ex}

>>>>

% \vspace{2ex}
% \begin{minipage}{\textwidth}
%     \centering
%     \hspace{-30pt}
%   \begin{minipage}[b]{0.44\textwidth}
%     \centering
%     \renewcommand{\arraystretch}{1.2}
%     \begin{tabular}[b]{l|l}
%             algorithm, 2D-3D& FLOPs\\
%                       & estimate\\
%             \hline\\
%             parametric plane & 585\\
%             normal plane (reuse) & 765\\
%             Moller and Trumbore & 783\\
%             Pl\"ucker (reuse) & 306
%     \end{tabular}
%     \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
%                       Only 2D-3D case considered.}
%     \label{tab:fundamental_flops}
%     \notePE{comment on different strategies}\noteJB{Rather put into text. I shall comment that.}
%   \end{minipage}
%   \hfil
%   \begin{minipage}[b]{0.5\textwidth}
%     \centering
%     \includegraphics[width=\textwidth]{\figpath intersections_fundamental_speed.pdf}
%     
%     \captionof{figure}{Efficiency of \plucker approach compared to the legacy \ngh code.}
%     \label{fig:fundamental_speed}
%     \end{minipage}
% \end{minipage}
% \vspace{2ex}

\begin{table}[!htb]
    \centering
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}[b]{l|l}
            algorithm, 2D-3D& FLOPs\\
                      & estimate\\
            \hline\\
            parametric plane & 585\\
            normal plane (reuse) & 765\\
            Moller and Trumbore & 783\\
            Pl\"ucker (reuse) & 306
    \end{tabular}
    \caption{Estimation of floating point operations count and comparison of different approaches.
             Only 2D-3D case considered.}
    \label{tab:fundamental_flops}
    \notePE{comment on different strategies}\noteJB{Rather put into text. I shall comment that.}
\end{table}

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.5\textwidth]{\figpath intersections_fundamental_speed.pdf}
    \caption{Efficiency of \plucker approach compared to the legacy \ngh code.}
    \label{fig:fundamental_speed}
\end{figure}
